---
title: "Fanstatstic Five - Team Introduction"
author: " Luke Vrotsos, Tyler Cheung, Kareena Legare, Shelby Tisdale, Ken Ye"
format:
  revealjs:
    scrollable: true
---

## Names

### Graduate Mentor

Luke Vrotsos

### Undergraduates

Tyler Cheung

Kareena Legare

Shelby Tisdale

Ken Ye

Nikita Daga

## Data

```{r}
#|echo: false
if (!require(pacman)) install.packages("pacman")
#> Loading required package: pacman
pacman::p_load(ChineseNames, tidyverse, corrplot, ggcorrplot)

data(givenname)
```

**givennames.csv**

1.  Potential Plots

    1.  Relationship between `name.gender` and `name.valence` (**scatterplot**) 

    2.  Relationship between `name.uniqueness` and `name.gender` (**scatterplot**)

    3.  Relationship between Avg. of `name.competence` and `bihua` (**scatterplot, points colored by gender**)

2.  Variables of Interest

    1.  `name.gender`

    2.  `name.valence`

    3.  `name.uniqueness`

    4.  `name.competence`

    5.  `bihua`(number of strokes in character)

    6.  `corpus.ppm`

    7.  `corpus.uniqueness` 

## EDA Part I

```{r}
  ggplot(givenname, aes(x = bihua, y = name.competence, color = name.gender, alpha = 0.5)) +
  geom_jitter() +
    labs(
      title = "Competence vs. bihua (number of strokes)",
      x = "Bihua",
      y = "competence"
    ) +
    theme_minimal()
```

```{r}
#|label: warmth v. decade visualization

# top 30 warmth
top30_warmth <- givenname |>
  arrange(-name.warmth) |>
  head(30)

# bottom 30 warmth
bottom30_warmth <- givenname |>
  arrange(name.warmth) |>
  head(30)

warmth_decade <- bind_rows(top30_warmth, bottom30_warmth) |>
  pivot_longer(cols = ppm.1930_1959:ppm.2000_2008, names_to = "decade",
               values_to = 'ppm_decade') |>
  mutate(decade = gsub("ppm.", "", decade),
         decade = case_when(decade == '1930_1959' ~ 'Before 1960',
                            decade == '1960_1969' ~ '1960s',
                            decade == '1970_1979' ~ '1970s',
                            decade == '1980_1989' ~ '1980s',
                            decade == '1990_1999' ~ '1990s',
                            decade == '2000_2008' ~ '2000s'),
         decade = fct_relevel(decade, 'Before 1960', after = 0)) 


warmth_decade |>
ggplot(aes(x = decade, y = ppm_decade, color = name.warmth)) +
  geom_jitter(alpha = 0.5) +
  theme_minimal() + 
  labs(x = "Decade",
       y = "PPM",
       title = "Frequency and Warmth of Chinese Characters Over Time")
```

## EDA Part II

```{r}
#| label: correlation-matrix-1

corr_names <- givenname |> 
  select(bihua, name.gender, name.ppm, name.uniqueness, name.valence, name.warmth,
         name.competence,
         corpus.uniqueness,
         corpus.ppm) |>
  cor(use = "pairwise.complete.obs") |>
  round(2) |> 
  corrplot(method = "number", number.cex = 0.7,
           type = "lower")


```

```{r}
#| label: correlation-matrix-2

names_corr <- givenname |>
  select(bihua, name.gender, name.ppm, name.uniqueness, name.valence, name.warmth,
         name.competence, corpus.ppm, corpus.uniqueness) |>
  as.matrix() |>
  cor()

names_p_vals <- cor_pmat(names_corr)


ggcorrplot(names_corr,
          type = "lower",
          method = "circle",
          show.legend = TRUE,
          legend.title = "Correlation Coefficient",
          p.mat = names_p_vals,
          colors = c("darkred", "white", "darkblue")) +
  annotate("text",
           color = "darkblue",
           x = 2.7, y = 7,
           size = 2.75,
           label = "Size of circle indicates \nstrength of positive correlation") +
  annotate("text",
           color = "darkred",
           x = 2.7, y = 6,
           size = 2.75,
           label = "X's indicate no significant \nrelationship (alpha > 0.05)") +
  labs(title = "Correlation Matrix of Chinese Name Characteristics")
```

## Research Questions

1.  How does name gender relate to warmth, competence, and valence of the name? 

2.  Is name competence related to bihua? (Start from here in our modeling)

3.  What is the correlation between tonation and alphabetical name preference with warmth, competence, and valence of the name?

4.  Time series of average given name warmth, competence, valence across 6 birth cohorts. 

5.  Given name tone (last digit of the \"pinyin\" variable, 1-4) vs. warmth, competence, valence...

6.  How has bihua of names changed over time?

## Modeling

```{r}
#|echo: false
tone_name <- givenname |>
  mutate(tone = as.factor(str_sub(pinyin, start= -1)),
         tone = if_else(tone %in% c('1', '2', '3', '4'), tone, '0'))
```

```{r}
m3 <- lm(name.competence ~ name.gender + bihua + relevel(factor(tone), ref = "4") + name.uniqueness + corpus.uniqueness, data = tone_name)
summary(m3)

car::vif(m3)
```
